---
title: "R Notebook"
output: html_notebook
---

Instantiates the driver object
```{r}
drv <- DBI::dbDriver("PostgreSQL")
```

Creates and opens a connection to the database implemented by the driver drv.
Connection string should be specified with parameters like user, password, dbname, host, port, tty and options
```{r}
con <- DBI::dbConnect(drv, host="localhost", 
                      port="5432", dbname="FIND", 
                      user="postgres", password="albamia") 
```

Provides List of connections handled by the driver
```{r}
DBI::dbListConnections(drv)
```

dbGetInfo(dbObject, ...) and summary(dbObject) returns information 
about the dbObject (driver, connection or resultSet)
```{r}
DBI::dbGetInfo(drv)
summary(con)
```

List of all tables in DB
```{r}
DBI::dbListTables(con)
```

Run an SQL statement by creating first a resultSet object.
Submits one statement to the database
```{r}
DBI::dbGetQuery(con, "SET NAMES 'utf8'")
```

Summary table total number of fish samples containing in FIND, with start and end date of the series
```{sql connection=con}
SELECT 
  MIN (s."Sample_Data") AS "start date",
  MAX (s."Sample_Data") AS "end date",
  COUNT (s."ITT") AS "n of fish samples",
  /*COUNT (s."ZOO) AS "n of zooplankton samples",
  COUNT (s."PHY) AS "n of phytoplankton samples",
  -- COUNT (s."COM) AS "n of ",
  COUNT (s."BEN) AS "n of benthos samples",
  COUNT (s."CHI) AS "n of chemistry samples",
  COUNT (s."MACRO) AS "n of macrophytes samples",
  -- COUNT (s."MICRO) AS "n of samples of ",*/
  l."Lake_Name"
FROM
  public."COM_Samples" AS s
  INNER JOIN public."COM_Lakes" AS l ON (s."ID_Lake" = l."ID_Lake")
WHERE
  s."ITT" = 1
GROUP BY
  l."Lake_Name"
```

Summary table total number of zooplankton samples containing in FIND, with start and end date of the series
```{sql connection=con}
SELECT 
  MIN (s."Sample_Data") AS "start date",
  MAX (s."Sample_Data") AS "end date",
  COUNT (s."ZOO") AS "n of zooplankton samples",
  l."Lake_Name"
FROM
  public."COM_Samples" AS s
  INNER JOIN public."COM_Lakes" AS l ON (s."ID_Lake" = l."ID_Lake")
WHERE
  s."ZOO" = 1
GROUP BY
  l."Lake_Name"
```

Summary table total number of zooplankton samples containing in FIND, with start and end date of the series
```{sql connection=con}
SELECT 
  MIN (s."Sample_Data") AS "start date",
  MAX (s."Sample_Data") AS "end date",
  COUNT (s."PHY") AS "n of phytoplankton samples",
  l."Lake_Name"
FROM
  public."COM_Samples" AS s
  INNER JOIN public."COM_Lakes" AS l ON (s."ID_Lake" = l."ID_Lake")
WHERE
  s."PHY" = 1
GROUP BY
  l."Lake_Name"
```

Summary table total number of zooplankton samples containing in FIND, with start and end date of the series
```{sql connection=con}
SELECT 
  MIN (s."Sample_Data") AS "start date",
  MAX (s."Sample_Data") AS "end date",
  COUNT (s."BEN") AS "n of benthos samples",
  l."Lake_Name"
FROM
  public."COM_Samples" AS s
  INNER JOIN public."COM_Lakes" AS l ON (s."ID_Lake" = l."ID_Lake")
WHERE
  s."BEN" = 1
GROUP BY
  l."Lake_Name"
```

Summary table total number of zooplankton samples containing in FIND, with start and end date of the series
```{sql connection=con}
SELECT 
  MIN (s."Sample_Data") AS "start date",
  MAX (s."Sample_Data") AS "end date",
  COUNT (s."CHI") AS "n of chemistry samples",
  l."Lake_Name"
FROM
  public."COM_Samples" AS s
  INNER JOIN public."COM_Lakes" AS l ON (s."ID_Lake" = l."ID_Lake")
WHERE
  s."CHI" = 1
GROUP BY
  l."Lake_Name"
```

Summary table total number of zooplankton samples containing in FIND, with start and end date of the series
```{sql connection=con}
SELECT 
  MIN (s."Sample_Data") AS "start date",
  MAX (s."Sample_Data") AS "end date",
  COUNT (s."MACRO") AS "n of macrophytes samples",
  l."Lake_Name"
FROM
  public."COM_Samples" AS s
  INNER JOIN public."COM_Lakes" AS l ON (s."ID_Lake" = l."ID_Lake")
WHERE
  s."MACRO" = 1
GROUP BY
  l."Lake_Name"
```
