---
title: "Some summury of FIND DB"
output: 
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    theme: flatly
author: "Alessandro Oggioni - 01 May 2020"
---

Instantiates the driver object
```{r}
library("RPostgreSQL")
drv <- DBI::dbDriver("PostgreSQL")
```

Creates and opens a connection to the database implemented by the driver drv.
Connection string should be specified with parameters like user, password, dbname, host, port, tty and options
```{r}
con <- DBI::dbConnect(drv, host="localhost", 
                      port="5432", dbname="FIND", 
                      user="postgres", password="albamia") 
```

Provides List of connections handled by the driver
```{r}
DBI::dbListConnections(drv)
```

dbGetInfo(dbObject, ...) and summary(dbObject) returns information 
about the dbObject (driver, connection or resultSet)
```{r}
DBI::dbGetInfo(drv)
summary(con)
```

### List of all tables in DB
```{r}
DBI::dbListTables(con)
```

Run an SQL statement by creating first a resultSet object.
Submits one statement to the database
```{r}
DBI::dbGetQuery(con, "SET NAMES 'utf8'")
```

### Total number of fish samples containing in FIND, with start and end date of the series
```{r}
DBI::dbGetQuery(con, "SET NAMES 'utf8'")
queryValueItt <- DBI::dbSendQuery(conn = con, statement = paste(
"SELECT 
  MIN (s.\"Sample_Data\") AS \"start date\",
  MAX (s.\"Sample_Data\") AS \"end date\",
  COUNT (s.\"ITT\") AS \"n of fish samples\",
  l.\"Lake_Name\"
FROM
  public.\"COM_Samples\" AS s
  INNER JOIN public.\"COM_Lakes\" AS l ON (s.\"ID_Lake\" = l.\"ID_Lake\")
WHERE
  s.\"ITT\" = 1
GROUP BY
  l.\"Lake_Name\""));
tblValueItt <- DBI::fetch(queryValueItt, n = -1)
DT::datatable(tblValueItt)
```

Summary table total number of zooplankton samples containing in FIND, with start and end date of the series
```{r}
DBI::dbGetQuery(con, "SET NAMES 'utf8'")
queryValueZoo <- DBI::dbSendQuery(conn = con, statement = paste(
"SELECT 
  MIN (s.\"Sample_Data\") AS \"start date\",
  MAX (s.\"Sample_Data\") AS \"end date\",
  COUNT (s.\"ZOO\") AS \"n of zooplankton samples\",
  l.\"Lake_Name\"
FROM
  public.\"COM_Samples\" AS s
  INNER JOIN public.\"COM_Lakes\" AS l ON (s.\"ID_Lake\" = l.\"ID_Lake\")
WHERE
  s.\"ZOO\" = 1
GROUP BY
  l.\"Lake_Name\""
));
tblValueZoo <- DBI::fetch(queryValueZoo, n = -1)
DT::datatable(tblValueZoo)
```

### Total number of phytoplankton samples containing in FIND, with start and end date of the series
```{r}
DBI::dbGetQuery(con, "SET NAMES 'utf8'")
queryValuePhy <- DBI::dbSendQuery(conn = con, statement = paste(
"SELECT 
  MIN (s.\"Sample_Data\") AS \"start date\",
  MAX (s.\"Sample_Data\") AS \"end date\",
  COUNT (s.\"PHY\") AS \"n of phytoplankton samples\",
  l.\"Lake_Name\"
FROM
  public.\"COM_Samples\" AS s
  INNER JOIN public.\"COM_Lakes\" AS l ON (s.\"ID_Lake\" = l.\"ID_Lake\")
WHERE
  s.\"PHY\" = 1
GROUP BY
  l.\"Lake_Name\""));
tblValuePhy <- DBI::fetch(queryValuePhy, n = -1)
DT::datatable(tblValuePhy)
```

### Total number of benthos samples containing in FIND, with start and end date of the series
```{sql connection=con}
SELECT 
  MIN (s."Sample_Data") AS "start date",
  MAX (s."Sample_Data") AS "end date",
  COUNT (s."BEN") AS "n of chemistry samples",
  l."Lake_Name"
FROM
  public."COM_Samples" AS s
  INNER JOIN public."COM_Lakes" AS l ON (s."ID_Lake" = l."ID_Lake")
WHERE
  s."BEN" = 1
GROUP BY
  l."Lake_Name"
```
**0 ROWS for benthos**

### Total number of chemistry samples containing in FIND, with start and end date of the series
```{sql connection=con}
SELECT 
  MIN (s."Sample_Data") AS "start date",
  MAX (s."Sample_Data") AS "end date",
  COUNT (s."CHI") AS "n of chemistry samples",
  l."Lake_Name"
FROM
  public."COM_Samples" AS s
  INNER JOIN public."COM_Lakes" AS l ON (s."ID_Lake" = l."ID_Lake")
WHERE
  s."CHI" = 1
GROUP BY
  l."Lake_Name"
```
**0 ROWS for chemistry**

### Total number of macrophytes samples containing in FIND, with start and end date of the series
```{sql connection=con}
SELECT 
  MIN (s."Sample_Data") AS "start date",
  MAX (s."Sample_Data") AS "end date",
  COUNT (s."MACRO") AS "n of macrophytes samples",
  l."Lake_Name"
FROM
  public."COM_Samples" AS s
  INNER JOIN public."COM_Lakes" AS l ON (s."ID_Lake" = l."ID_Lake")
WHERE
  s."MACRO" = 1
GROUP BY
  l."Lake_Name"
```
**0 ROWS for chemistry**